HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-03 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``The reliability of the data is important for the use of this data by third parties. Please explain in detail how the human processing was done. Also, to what extent can machine failures be included in image processing ? Do humans correct them ?''} \medskip

	\textbf{Author response:} We thank the referee for this remark. Regarding the data-acquisition pipeline presented in Section 2, the human actions are limited. The only human processing comes at the step where the fashion trends are defined. The features are automatically detected by the vision recognition models. Then, we only define trends that are relevant for the fashion industry. For instance, the A-line dress is identified where a dress is detected with a particular length, a particular shape and a particular collar shape, all of these details detected with different models. These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper. 
Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set. Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed. Please note that the data acquisition pipeline has been detailed and extended in Section 2. \\

	\item {\em ``In publishing the data, it would be good to add a little more analysis of the characteristics of the data. For example, basic statistics for each market, statistics for the Weak signal $w^{f,i}_t$, etc.''} \medskip

	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset. So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately. \\

### 2023-07-03 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Minor updates review + answer R3

During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor results and instability. In this paper, a more general framework able to deal with any kind of per-time-series models is provided. \textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series. The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously. For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations. Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}

@@

For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In some cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is mostly unknown. This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.

@@

\begin{table}
  \caption{Results summary on the 10000 time series of the fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed. \textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}}
  \centering
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws*} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws*} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws*}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
  \end{tabular}
\label{tab:metricresults}
\end{table}

@@

\begin{table}
  \caption{Results summary on 1000 time series and 100 time series of the fashion dataset. The MASE average on all the time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed. \textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}\vspace{0.5cm}}
 \centering
 \resizebox{1.\textwidth}{!}{ 
 \begin{tabular}{l||lllll|lllll}
   \multicolumn{11}{c}{1000 time series fashion dataset}\vspace{0.5cm}\\
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
      \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\

@@

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose  a new hybird model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent and understand fashion through its representation on social media. Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.

>>>>

During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor results and instability. In this paper, a more general framework able to deal with any kind of per-time-series models is provided. \textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series. The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously. For instance, hidden Markov models provide a very interesting framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations. Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}

@@

For non stationary time series, changes of behaviours are not always predictable using the past of the sequence. In some cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is mostly unknown. This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.

@@

\begin{table}
  \caption{Results summary on the 10000 time series of the fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed. \textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}}
  \centering
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws*} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws*} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws*}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
  \end{tabular}
\label{tab:metricresults}
\end{table}

@@

\begin{table}
  \caption{Results summary on 1000 time series and 100 time series of the fashion dataset. The MASE average on all the time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed. \textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}\vspace{0.5cm}}
 \centering
 \resizebox{1.\textwidth}{!}{ 
 \begin{tabular}{l||lllll|lllll}
   \multicolumn{11}{c}{1000 time series fashion dataset}\vspace{0.5cm}\\
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
      \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\

@@

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose  a new hybird model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data. }% Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.} 
 By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.
